### 2017-05-31 doc/response.tex

\newpage
\pagenumbering{roman}

\noindent
Dear Dr.~Merlo,
\newline

Thank you for the very helpful suggestions and insightful questions
posed in this review.  We apologize for the delay getting this
revision back to you and very much appreciate the extension you 
gave us to resubmit the manuscript.

We have substantially revised the article in response to your and the reviewers' 
comments. Specifically with regard to the two main issues you raised, we have 
introduced a uni-modal language model (referred to as the {\sc LM} model in the text) 
and reported the results of all the experiments on this model as well. Also following 
your recommendation, we have removed the exploratory parts of (the old) Section 6, 
and reorganized the paper by merging previous Sections 4, 5 and the remaining of 
Section 6 into a single section containing all the experiments (that is Section 4 in the 
revised manuscript). We have kept and expanded the quantitative analysis of the nature of 
n-gram contexts that trigger individual dimensions in the hidden layers; this experiment is 
now reported in Section~\ref{sec:contexts}.

Furthermore, we have made clarifications about the details of the techniques all 
through the manuscript, expanded Introduction (Section~\ref{sec:intro}) to 
emphasise our contributions, updated Related Work (Section~\ref{sec:related}) 
to include relevant papers that came out while this manuscript was under review, and expanded Discussion (Section~\ref{sec:conclusion}) to discuss in more detail the relevance and generalizability of our techniques.

@@

- In terms of clarity, I would appreciate a better description of the
  IMAGINET model, which is being analyzed. The model is described in
  terms of its equations, but I would like to see a better
  presentation of what is the intent behind it -

- what is being modeled and what is being learned? this is available
  in the original IMAGINET paper, but I think the description should
  be imported to this paper also, in order to make it self contained
  and stronger.

\end{verbatim}  
\begin{quote}
\textsc{Author Response:}
We have expanded Section~\ref{sec:imaginet} with a conceptual
description of {\sc Imaginet} and its learning goals, and added a graphical
representation of the structure of the model for more clarity (Figure~\ref{fig:imaginet}).
\end{quote}
\begin{verbatim}

- Also in terms of clarity, the graphs are not described in enough
  detail in my view. Whiel the box plots (figure 2 and others) are
  somewhat standard, they are not mainstream in the NLP commuity, and
  I would appreciate seeing a more detailed description in the main
  text or the caption of what each component means, both generally and
  in the context of the specific graph.
\end{verbatim}  
\begin{quote}
\textsc{Author Response:}  \todo[inline]{explain the updated graph}
\end{quote}
\begin{verbatim}
- Figure 7 is confusing -- what are the different colors between,
  e.g., the words "in" and "tree" in the first line, and between "a"
  and "wii" in the second? I assume this is some "gradient" between
  two colors, but it looks like there are several data points and is
  very confusing. Please fix this.
\end{verbatim}  
\begin{quote}
\textsc{Author Response:}  Following the recommendation of the reviewers,
we shortened the original Section 6 and removed this figure.
\end{quote}
\begin{verbatim}

@@

In terms of content:

- In section 6.1, why is the sorting by magnitude and not by absolute
  value? are negative activations not important?
\end{verbatim}  
\begin{quote}
\textsc{Author Response:}  It was in fact the absolute value of the activations 
that was taken into account. In the revised manuscript, we have removed this 
and other exploratory experiments and expanded the quantitative analyses.
\end{quote}
\begin{verbatim}

- When choosing the "top k context of each unit" (section 6.1), it is
  not clear what a "unit" is and how it is chosen.
\end{verbatim}  
\begin{quote}
\textsc{Author Response:}  A unit is one individual dimension in the final hidden layer 
of the network. We have made this clear in the revised text.
\end{quote}
\begin{verbatim}

- I did not understand the last sentence in section 6.1, and would
  appreciate an elaboration on this point (or a removal).
\end{verbatim}  
\begin{quote}
\textsc{Author Response:}  We removed this part and added an expanded discussion of the generalizability of our techniques to Discussion (Section~\ref{sec:conclusion}).
\end{quote}
\begin{verbatim}

- In section 6.2, it is not clear how trigrams with high activations
  are chosen. How is a trigram with high activation defined? this is
  not clear from the description of the method.
\end{verbatim}  
\begin{quote}
\textsc{Author Response:} We have removed this section in the revised manuscript. We 
address the nature of contexts which trigger individual dimensions and a systematic
procedure for selecting the dimensions themselves in more detail now in 
Section~\ref{sec:contexts}.
\end{quote}
\begin{verbatim}

- I am not convinced by the experiments in section 6.3 and their
  importance -- either they are not described properly and I missed
  something, or they are somewhat meaningless: when training a
  logistic regression model to predict grammatical function, it is not
  surprising that ones finds units that are predictive of grammatical
  function.
\end{verbatim}  
\begin{quote}
\textsc{Author Response:}  As mentioned before, we have reorganised 
the experiments and remove the exploratory parts, including the old Section 6.3. 
We address the issue of encoding grammatical functions in the revised manuscript in 
Sections ~\ref{sec:beyondlexical} (specifically in \ref{sec:gramfunc}).
\end{quote}
\begin{verbatim}

@@

~ Where is section 6.4?

\end{verbatim}  
\begin{quote}
\textsc{Author Response:} It was there, believe us! But we have removed this 
experiment from the revised version for the sake of clarity and coherence of our analyses.
\end{quote}
\begin{verbatim}

@@

Revisions to be Encouraged:
:

5 Minor Revisions Required [Help]
:

See the points marked with (-) in the weaknesses above. Points marked
with (~) are less important. For section 6.3, my recommendation is
that it is either substantially revised, or removed altogether -- I
believe the paper has enough merit without it.

\end{verbatim}  
\begin{quote}
\textsc{Author Response:}  We hope we have addressed all your comments and concerns. We have removed the experiments in (the old) Section 6.3 from the revised manuscript.
\end{quote}
\begin{verbatim}

@@

6 Typographic Errors [Help]
:

- "by as" in the first sentence of the intro.

- There are some cases of using parenthesis in citation where they
  shouldn't be, for example the first two citations in section 2 ("of
  (Elman 1990)" should be "of Elman (1990)").

\end{verbatim}  
\begin{quote}
\textsc{Author Response:} The typo and the citation inconsistencies are fixed.
\end{quote}
\begin{verbatim}

@@

Strengths:
: 
* neat idea and novel contribution (pairing activations with POS and
dependency relations to gain further insights into RNNs)

* extensive analysis; especially going beyond lexical cues (Section
5.3), where the authors train a regression model to predict omission
scores on a token level, showing that the network not just learns to
rely on word types, but it also learns position information
(particularly important for the textual pathway)

Weaknesses:
: 
* the description of the top K contexts is not clear, how are top k
contexts calculated? do you find the most active token (highest
absolute value of hidden activation in the sequence?) and then use
the words around it to find the trigrams? (what is meant by 'each
unit' in Section6.1? Is the matrix actually R^nxd?); maybe you sort
by column, not row?

\end{verbatim}  
\begin{quote}
\textsc{Author Response:}  You are absolutely right about the description of 
top k contexts being confusing. We have removed this part and reorganized 
the experiments section (Section~\ref{sec:experiments}) to make it more understandable
and coherent. 
\end{quote}
\begin{verbatim}

@@

\end{verbatim}  
\begin{quote}
\textsc{Author Response:}  Following your and others' suggestion, we have removed this section from the revised manuscript.
\end{quote}
\begin{verbatim}

4 Substantive Revisions Required [Help]

Complete this section if either 'Revise and Resubmit' or 'Reject' has
been recommended.

Revisions to be Required:
: 
- clearer description of how top k contexts are obtained
\end{verbatim}  
\begin{quote}
\textsc{Author Response:}  As mentioned above, we have removed this part and reorganized Section~\ref{sec:experiments} to make our analyses more concrete and clear.
\end{quote}
\begin{verbatim}

Revisions to be Encouraged:
: 
- figures are not readable in BW printing; in addition to color, use
  different symbols/line types
\end{verbatim}  
\begin{quote}
\textsc{Author Response:}  We have reformatted many of our figures to make them more readable.
\end{quote}
\begin{verbatim}

@@

- Related Work: clarify better how you differ from Li et al. (2015),
  you mention "for a comparative analysis": I interpret this as "we
  analyze a multi-task learning model (visual / textual) and compare
  what the two parts learn"
\end{verbatim}  
\begin{quote}
\textsc{Author Response:} We have edited our related work section to make the comparison more 
clear. In addition to taking into account tasks that rely on different modalities (language as well as vision), 
we focus more on learning structural properties of the input, whereas Li et al. (2015) focus on single
tokens.
\end{quote}
\begin{verbatim}

5 Minor Revisions Required [Help]
: 
- Sec 2, clarify: what are 'negative strings'? (non-words?)
\end{verbatim}  
\begin{quote}
\textsc{Author Response:}  we have reworded `positive' and `negative' as `grammatical' 
and `ungrammatical' to avoid confusion.
\end{quote}
\begin{verbatim}
- Before equation 9 missing lambda ("weighted by \lambda"; what lambda
  is used in the exp.?)
\end{verbatim}  
\begin{quote}
\textsc{Author Response:}  There was no $\lambda$ in that equation, but in 
Section~\ref{sec:imaginet} we report the value we use for the parameter 
$\alpha$ in Equation~(\ref{eq:losscombo}).
\end{quote}
\begin{verbatim}
- it would be helpful to include a figure of model (as in original
  paper)
\end{verbatim}  
\begin{quote}
\textsc{Author Response:}  We have included an illustration of the structure of the 
model in Figure~\ref{fig:imaginet}.
\end{quote}
\begin{verbatim}
- "two minor modifications" but the first seems you also use cosine,
  was that different previously, not clear.
\end{verbatim}  
\begin{quote}
\textsc{Author Response:}  You are right, the description of the model in 
Section~\ref{sec:imaginet} presents the version used in this paper, which uses 
cosine distance. The original Imaginet model uses mean square error instead; 
we clarified this issue in footnote~\ref{ft:imaginet}.  
\end{quote}
\begin{verbatim}
- specify interaction features in regression model
\end{verbatim}  
\begin{quote}
\textsc{Author Response:}  We have specified the interaction features used in each regression model in Section~\ref{sec:beyondlexical}.
\end{quote}
\begin{verbatim}
- 5.3.1. why also 'water'?
\end{verbatim}  
\begin{quote}
\textsc{Author Response:}  We have removed {\it water} from the set of examples 
in Figure~\ref{fig:top_words}.
\end{quote}
\begin{verbatim}

6 Typographic Errors [Help]
: 
- abstract: sentence "Based on.." way too long
- mention multi-task in abstract
- introduction: "this includes various" > "This can be applied to
  various"
- from linguistic point (missing det)
- generally avoid long sentences (e.g., last paragraph sec 5.1,
  sec. 5.2)
- rephrase: "this model we refer to as SUM"
- windowsizes
\end{verbatim}  
\begin{quote}
\textsc{Author Response:}  We have fixed these issues, thanks for bringing them to our attention.
\end{quote}
\begin{verbatim}

@@

3 Strengths and Weaknesses [Help]

Strengths:
: 
This paper makes a useful methodological contribution by proposing
methods to analyze the knowledge learned by neural networks, which is
an underexplored area, at least for networks trained on text data. The
paper is well written, and technically sound.

Weaknesses:
: 
The results of the paper are unfortunately fairly obvious. From the
omission score analysis, we learn that a model trained to predict the
next word in a sentence is sensitive to function words, while a word
trained to associate a sentence with an image representation (which is
essentially the output of the object detector) pays more attention to
nouns. This is not at all surprising, it just reflects the different
training objectives. The fact that the hidden units respond to
specific n-grams is also expected; most people already believe that
RNNs are good at approximating n-gram models; the question is, can
they model more elaborate syntactic structures?
\end{verbatim}  
\begin{quote}
\textsc{Author Response:}  \todo[inline]{address}
\end{quote}
\begin{verbatim}

This is really the question that the authors should explore, e.g., by
testing whether the model can learn long distance dependencies,
agreement, recursion, word order. An example for recent work that goes
in this direction is Linzen et al. (2016).
\end{verbatim}  
\begin{quote}
\textsc{Author Response:} We have expanded the related work 
(Section~\ref{sec:related}) with a discussion of Linzen et al. (2016) 
and a few other relevant articles that came out while our submission was under review.
\end{quote}
\begin{verbatim}

Another limitation of the paper is its focus on one particular model,
which happens to be the authors'. To be convincing, the paper would
really need to compare results for this model with results for other
architectures, showing that the proposed analysis methods offer real
discriminative power.
\end{verbatim}  
\begin{quote}
\textsc{Author Response:}  Due to space and time limitations we have to 
leave the comparison with other architectures for future work; however we 
have expanded the discussion of the generalizability of our techniques to other
architectures in Discussion (Section~\ref{sec:conclusion}).
\end{quote}
\begin{verbatim}

@@

Related to this, it is not clear to me why a multimodal, multitask
model such as Imaginet is required for the work presented
here. Surely, similar results would be obtained if two unimodal RNN
models were trained, one on image descriptions to predict the next
word, and one on image representations to predict the description.
\end{verbatim}  
\begin{quote}
\textsc{Author Response:}  \todo[inline]{address}
\end{quote}
\begin{verbatim}

4 Substantive Revisions Required [Help]

Complete this section if either 'Revise and Resubmit' or 'Reject' has
been recommended.

Revisions to be Required:
: 
(1) Add comparisons to unimodal models (or at least to unimodal
versions of Imaginet).
\end{verbatim}  
\begin{quote}
\textsc{Author Response:}  In the revised manuscript we have introduced a uni-modal language model, and updated all of our experiments to include this model as well.
\end{quote}
\begin{verbatim}

(2) Add comparisons to other architectures (LSTMs, etc.)
\end{verbatim}  
\begin{quote}
\textsc{Author Response:}  As we mentioned before, we are very interested in 
applying our proposed techniques to other tasks and architectures in future work. 
For the sake of this manuscript, we have included a theoretical discussion of how 
these techniques can be implemented for a number of other architectures (see 
Section~\ref{sec:conclusion}).
\end{quote}
\begin{verbatim}

### 2017-05-31 doc/categories.tex
Boxplot explanation.

The omission scores can be used not only to
estimate the importance of individual words, but also of syntactic
categories. We estimate the salience of each syntactic category by
accumulating the omission scores for all words in that category. We
tag every word in a sentence with the part-of-speech (POS) category
and the dependency relation (deprel) label of its incoming arc. For
example, for the sentence \emph{the black dog}, we get ({\it
  the},~DT,~det), 
({\it black},~JJ,~amod), ({\it dog},~NN,~root). 
Both POS tagging and dependency parsing are performed 
using the  dependency parser from the Spacy package.\footnote{Available at
  \url{https://spacy.io/}.} 
%The POS tags used are the Penn Treebank tags and the dependencies are 
%the Stanford basic dependencies.

Figure~\ref{fig:omission-imaginet} shows the distribution of omission
scores per POS and dependency label for the two pathways of {\sc
  Imaginet} and for {\sc LM}.  The general trend is that for the {\sc
  Visual} pathway, the omission scores are high for a small subset of
labels - corresponding mostly to nouns, less so for adjectives and
even less for verbs - and low for the rest (mostly function words and
various types of verbs). For {\sc Textual} the differences
are \label{edit:textualomission} smaller, and the pathway seems to be
sensitive to the omission of most types of words.  For {\sc LM} the
distribution over categories is also relatively uniform, but the omission scores are higher
overall than for {\sc Textual}.

>>>>

The omission scores can be used not only to
estimate the importance of individual words, but also of syntactic
categories. We estimate the salience of each syntactic category by
accumulating the omission scores for all words in that category. We
tag every word in a sentence with the part-of-speech (POS) category
and the dependency relation (deprel) label of its incoming arc. For
example, for the sentence \emph{the black dog}, we get ({\it
  the},~DT,~det), 
({\it black},~JJ,~amod), ({\it dog},~NN,~root). 
Both POS tagging and dependency parsing are performed 
using the  \verb+en_core_web_md+ dependency parser from the Spacy package.\footnote{Available at
  \url{https://spacy.io/}.} 
%The POS tags used are the Penn Treebank tags and the dependencies are 
%the Stanford basic dependencies.

Figure~\ref{fig:omission-imaginet} shows the distribution of omission
scores per POS and dependency label for the two pathways of {\sc
  Imaginet} and for {\sc LM}.\footnote{The boxplots in this and
  subsequent figures are Tukey boxplots and should be interpreted as follows: the box extends
from the 25th to the 75th percentile of the data; the line across the
box is the 50th percentile, while the whiskers extend past the lower
and upper quartile to $1.5\times$
the interquartile range (i.e.\ 75th percentile - 25th percentile); the
points are outliers.}  The general trend is that for the {\sc
  Visual} pathway, the omission scores are high for a small subset of
labels - corresponding mostly to nouns, less so for adjectives and
even less for verbs - and low for the rest (mostly function words and
various types of verbs). For {\sc Textual} the differences
are \label{edit:textualomission} smaller, and the pathway seems to be
sensitive to the omission of most types of words.  For {\sc LM} the
distribution over categories is also relatively uniform, but the omission scores are higher
overall than for {\sc Textual}.
